\thetitle

### 2020-10-20 sun_phases/spin_qudit_tomo.tex
added statement of 2d-1 conjecture in the language of classical signal recovery

\documentclass[nofootinbib,notitlepage,twocolumn]{revtex4-2}

@@

Finally, for any fixed degree $\ell$, finding solutions to the reduced recovery problem in Eq.~\eqref{eq:tomo_recovery} is equivalent to recovery of a function in the degree-$\ell$ subspace of $L^2\p{\Omega_2}$, which is possible with $\abs{V}=2\ell+1$ samples (equal to the dimension of the degree-$\ell$ subspace) \cite{freeden2008spherical}.
In our case, the degree $\ell$ takes a maximal value of $\ell_{\t{max}}\equiv d-1$, so state recovery requires at least as many measurement axes as there are transition operators with degree $\ell_{\t{max}}$, namely $2\ell_{\t{max}}+1=2d-1$.
Since
\begin{enumerate*}
\item there are only $2\ell+1\le2d-1$ transition operators of degree $\ell\le\ell_{\t{max}}$, and
\item measuring spin projections along any axis simultaneously provides measurement data for transition operators of all degrees $\ell\le\ell_{\t{max}}$,
\end{enumerate*}
one might expect that $2d-1$ suitably chosen measurement axes would always suffice to perform full tomography of a $d$-level spin qudit.
Unfortunately, we have no general proof of this conjecture, which may require a deeper analysis of fixed-degree signal recovery on the sphere.
Nonetheless, in the following section we show by example that $2d-1$ measurement axes suffice for all $d\le20$.

>>>>

\documentclass[notitlepage,twocolumn]{revtex4-2}

@@

Finally, for any fixed degree $\ell$, finding solutions to the reduced recovery problem in Eq.~\eqref{eq:tomo_recovery} is equivalent to recovery of a function in the degree-$\ell$ subspace of $L^2\p{\Omega_2}$, which is possible with $\abs{V}=2\ell+1$ samples (equal to the dimension of the degree-$\ell$ subspace) \cite{freeden2008spherical}.
In our case, the degree $\ell$ takes a maximal value of $\ell_{\t{max}}\equiv d-1$, so state recovery requires at least as many measurement axes as there are transition operators with degree $\ell_{\t{max}}$, namely $2\ell_{\t{max}}+1=2d-1$.
Since
\begin{enumerate*}
\item there are only $2\ell+1\le2d-1$ transition operators of degree $\ell\le\ell_{\t{max}}$, and
\item measuring spin projections along any axis simultaneously provides measurement data for transition operators of all degrees $\ell\le\ell_{\t{max}}$,
\end{enumerate*}
one might expect that $2d-1$ suitably chosen measurement axes would always suffice to perform full tomography of a $d$-level spin qudit.
In the language of classical signal recovery, we would expect there to exist a set of $2\ell_{\t{max}}+1$ points on the sphere that enable the recovery of any degree-$\ell$ function with $\ell\le\ell_{\t{max}}$ (given prior knowledge of $\ell$) \footnote{We could further conjecture that if {\it any} set of points $V\subset\Omega_2$ enables the recovery of degree-$\ell_{\t{max}}$ functions on the sphere, then $V$ would allow recovery degree-$\ell$ functions with $\ell\le\ell_{\t{max}}$.  However, this condition is stronger than that necessary to guarantee full recovery of a $d$-level spin qudit state with $2d-1$ measurement axes.}.
Unfortunately, we have no general proof of this conjecture, which may require a deeper analysis of fixed-degree signal recovery on the sphere.
Nonetheless, in the following section we show by example that $2d-1$ measurement axes suffice for all $d\le20$.
